Automatically generated NE tagged corpora for English and Hungarian

### 2012-06-27 paper/engNERwiki.tex
Order of authors fixed.

\author{Dávid Márk Nemeskey \\
  Research Institute for \\ Computer Science and Automation \\
  Hungarian Academy of Sciences \\
  H-1111 Kende utca 13-17, Budapest \\
  {\tt nemeskey.david@sztaki.mta.hu} \\\And
  Eszter Simon \\
  Research Institute for Linguistics \\
  Hungarian Academy of Sciences \\
  H-1068 Benczúr utca 33, Budapest \\
  {\tt simon.eszter@nytud.mta.hu} \\}

>>>>

\author{Eszter Simon \\
  Research Institute for Linguistics \\
  Hungarian Academy of Sciences \\
  H-1068 Benczúr utca 33, Budapest \\
  {\tt simon.eszter@nytud.mta.hu} \\\And
  Dávid Márk Nemeskey \\
  Research Institute for \\ Computer Science and Automation \\
  Hungarian Academy of Sciences \\
  H-1111 Kende utca 13-17, Budapest \\
  {\tt nemeskey.david@sztaki.mta.hu} \\}
